---
title: "Gender_Gap_TED"
author: "Aanchal Setia"
date: "2024-09-25"
output: html_document
---

```{r setup, include=FALSE}
# Load necessary libraries
p_load(readr)       
p_load(dplyr)       
p_load(MASS)       
p_load(sjPlot)
p_load(stm)         
p_load(quanteda)
p_load(scales)
p_load(ggplot2)    
p_load(tidyr)      
p_load(ggpubr)      
p_load(purrr)      
p_load(corrplot)   
p_load(interactions)
p_load(wordcloud)
```

## Reading, Cleaning & Merging Datasets 

```{r}
# Reading the main dataset containing TED Talk transcripts
Ted <- read_csv("~/Documents/TEDTALK/Ted.csv")

# Reading the file with gender annotations (manual coding of speaker gender)
Coding <- read_csv("~/Documents/TEDTALK/TEDTalks_URA_Annotations - URA TEDTalks Annotation.csv")

```
Checking and Manipulating Date Variables
```{r}
# Checking the class of the variable 'published_timestamp' to confirm it’s in date format
class(Ted$published_timestamp)

# Extracting the year from the 'published_timestamp' and saving it in a new variable 'year'
Ted$year <- format(Ted$published_timestamp, "%Y")

```
Subsetting Columns of Interest
```{r}
# Subsetting columns of interest from the 'Ted' dataset (specific columns: 2, 3, 4, 6, 7, 62, 63, 203)
Ted <- Ted[, c(2, 3, 4, 6, 7, 62, 63, 85, 203)]
```
Merging Data and Recoding Gender
```{r}
# Merging the 'Coding' and 'Culture' datasets based on 'talk__id' (unique identifier for each TED Talk)
# The 'all = TRUE' ensures all rows are retained in the merge, even if no match is found in either dataset
merged_data <- merge(Coding, Ted, by = "talk__id", all = TRUE)

# Recoding gender values to standardize the labels (e.g., 'F' becomes 'Female', 'males' becomes 'Male', etc.)
merged_data$recode_gender <- dplyr::recode(merged_data$speaker_gender, 
                                     "F" = "Female",
                                     "males" = "Male",
                                     "M" = "Male",
                                     "male" = "Male",
                                     "woman" = "Female",
                                     "female" = "Female",
                                     "nonbinary" = "non-binary")
# Keeping only rows where gender is either 'Male' or 'Female' (excluding non-binary and missing data)
merged_data <- subset(merged_data, merged_data$recode_gender == "Male" | merged_data$recode_gender == "Female")

# Displaying a frequency table of the recoded gender variable
table(merged_data$recode_gender)
##Removing Rows with Missing Values

# Removing rows where the 'transcript' column has missing values (NA)
merged_data <- merged_data[!is.na(merged_data$transcript), ]

# Removing rows where the 'like_count' column has missing values (NA)
merged_data <- merged_data[!is.na(merged_data$like_count), ]



# Reading the results from the transcript (which generated tags for the TED Talks)
ted <- read_csv("~/Downloads/results.csv")

# Removing rows where 'talks__tags' column has missing values (NA)
ted <- ted[!is.na(ted$talks__tags), ]

# Subsetting columns to keep only 'talk__id' and 'talks__tags' 
ted <- ted[,c(3,6)]

# Merging the 'merged_data' with the ted data based on 'talk__id' (the unique identifier for TED Talks)
ted <- merge(merged_data, ted, by = 'talk__id')

# Removing rows where 'talks__tags' is missing (NA)
ted <- ted[!is.na(ted$talks__tags),]
```
Preparing Document Feature Matrix (DFM)
```{r}
# Create a Document Feature Matrix (DFM) using tokenized TED Talk tags
myDfm <- dfm(tokens_remove(

    tokens(ted$talks__tags, remove_punct = TRUE),

    stopwords("en")

  ),

  tolower = TRUE

)
```
Choosing Optimal Number of Topics (K)
```{r}
# Perform a search for optimal K (number of topics) using the searchK function.
# K values are tested between 3 and 30 topics, with a sample size of 1000 documents.
differentKs <- searchK(myDfm,     
                       K = c(3:30),
                       N = 1000,
                       data = ted$talks__tags,
                       max.em.its = 1000,
                       init.type = "Spectral")
```
Visualizing Model Fit Metrics
```{r}
# Convert the results into a tidy format for visualization

plot_data <- differentKs$results %>%
  pivot_longer(cols = -K, names_to = "metric", values_to = "value") %>%
  filter(metric %in% c("lbound", "heldout", "residual", "semcoh")) %>%
  mutate(value = map_dbl(value, ~ .[1])) %>%
  mutate(K = map_dbl(K, ~ .[1]))

# Plot the model fit metrics (log likelihood, held-out likelihood, residuals, etc.) for different values of K
ggplot(plot_data, aes(x = K, y = value, color = metric)) +
  geom_point() +
  geom_line() +
  geom_vline(xintercept = c(18, 20, 23, 30), linetype = "solid", color = "black") +
  scale_x_continuous(breaks = c(18, 20, 23, 30)) +
  facet_wrap(~metric, scales = "free") +
  labs(x = "Number of Topics (K)", y = "Metric Value") +
  theme_pubr() +
  theme(legend.position = "bottom", legend.title = element_blank())
```

Running the STM Model with K = 20
```{r}
# Selecting the number of topics (K = 20) based on the visualized metrics
tag_topic_20 <- stm(myDfm, K = 20,
                    verbose = FALSE, seed = 1234, init.type = "Spectral")

# Displaying the summary of the STM model
summary(tag_topic_20)

```

Estimating the Effect of Gender on Topic Prevalence
```{r}
# Estimate the effect of gender on topic prevalence using the estimateEffect function
# This models the prevalence of each topic (1 to 20) as a function of speaker gender
mes20 <- estimateEffect(formula = 1:20 ~ recode_gender,
                        stmobj = tag_topic_20,
                        metadata =ted)

# Displaying the summary of the estimated effects
summary(mes20)
```
Calculating and Plotting Average Topic Probabilities
```{r}
# Extract the document-topic proportions (theta matrix) and convert it to a data frame
doc_topic_p20 <- as.data.frame(tag_topic_20$theta)

# Combine the document-topic probabilities with the original dataset 
ted20 <- cbind(ted, doc_topic_p20)

# Converting gender and year to factor and numeric variables for further analysis
ted20$recode_gender <- as.factor(ted20$recode_gender)
ted20$year <- as.numeric(ted20$year)

# Renaming the gender variable for clarity
ted20 <- ted20 %>%
  rename(Gender = recode_gender)

#Identifying the Dominant Topic for Each Document

# Finding the dominant topic for each document (i.e., the topic with the highest probability for each document)
ted20$dominant_topic <- apply(ted20[, 22:41], 1, which.max)

#Calculating and Plotting Average Topic Probabilities
# Calculate the average topic probability for documents with each dominant topic
avg_probs <- ted20 %>%
  group_by(dominant_topic) %>%
  summarise(across(V1:V20, mean, na.rm = TRUE))

# Optionally, calculate the average probability for all topics across all documents
avg_probs_all <- ted20 %>%
  summarise(across(V1:V20, mean, na.rm = TRUE))

# Reshape the average probabilities data for visualization
avg_probs_long <- avg_probs %>%
  pivot_longer(cols = V1:V20, names_to = "Topic", values_to = "Average_Probability") %>%
  mutate(Type = "Dominant Topic")

avg_probs_all_long <- avg_probs_all %>%
  pivot_longer(cols = V1:V20, names_to = "Topic", values_to = "Average_Probability") %>%
  mutate(Type = "All Topics")

# Combine both datasets (dominant vs all topics) for plotting
plot_data <- bind_rows(avg_probs_long, avg_probs_all_long)

# Plot the average topic probabilities
ggplot(plot_data, aes(x = Topic, y = Average_Probability, fill = Type)) +
  geom_bar(stat = "identity", position = "dodge", alpha = 1) +
  labs(title = "Average Topic Probabilities: Dominant vs All Topics",
       x = "Topic",
       y = "Average Probability") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

```

Creating a Correlation Matrix for Topics
```{r}
# Creating a correlation matrix for the topic proportions (V1 to V20)
correlation_matrix <- cor(ted20[, paste0("V", 1:20)], use = "pairwise.complete.obs")

# Plotting the correlation matrix with significance levels
corrplot(correlation_matrix, method = "circle", type = "upper", sig.level = 0.05, tl.col = "black", tl.srt = 45)

```

Word Clouds

```{r}
#This code generates word clouds for seven topics identified by the STM model, using the cloud() function and a custom color palette. Topics like AI & Robotics, Cognitive Science, Social Justice, Personal Growth, Gender & Sexuality, Mental Health, and Culture are represented. Each word cloud includes up to 12 high-frequency words (except Culture, which has 50), providing a visual representation of the terms most closely associated with each topic.

# Word Clouds

# Define your color palette
my_colors <- c("#003366", "#004d00", "#b30000", "#0033cc", "#990000")

# Create the word cloud with proper scaling for term frequencies
AIRobotics <- cloud(tag_topic_20, topic = 20, type = "model", max.words = 12, colors = my_colors)
CogSci <- cloud(tag_topic_20, topic = 6, type = "model", max.words = 12, colors = my_colors)
SocialJustice <- cloud(tag_topic_20, topic = 10, type = "model", max.words = 12, colors = my_colors)
PersonalGrowth <- cloud(tag_topic_20, topic = 12, type = "model", max.words = 12, colors = my_colors)
GenderSexuality <- cloud(tag_topic_20, topic = 14, type = "model", max.words = 12, colors = my_colors)
MentalHealth <- cloud(tag_topic_20, topic = 15, type = "model", max.words = 12, colors = my_colors)
Culture <- cloud(tag_topic_20, topic = 17, type = "model", max.words = 50, colors = my_colors)

```

Statistical Analyses

```{r}
#This code performs statistical analyses for various TED Talk topics (AI & Robotics, Cognitive Science, Social Justice & Activism, Personal Growth, Gender & Sexuality, Mental Health, and Culture). Generalized linear models (negative binomial regressions) are fitted to examine the interaction of year and gender on the number of likes received, with duration as a control variable. Interaction plots are generated for each topic, with gender represented by red (female) and blue (male), and confidence intervals included.



# Statistical Analyses

# AI Related Topic
AIandRobotics <- subset(ted20, ted20$dominant_topic == '5')
AIandRobotics <- glm.nb(like_count ~ year * Gender + duration + fame_google , data = AIandRobotics)
summary(AIandRobotics)
plot_AI <- interact_plot(AIandRobotics, 
                         pred = year, 
                         modx = Gender,  
                         plot.points = FALSE,
                         interval = TRUE,           
                         colors = c("red", "blue"))

final_plot_AI <- plot_AI + labs(x = "Year",                
               y = "Number of Likes",     
               color = "Gender") +        
  scale_color_manual(labels = c("Female", "Male"), values = c("red", "blue")) + 
  scale_fill_manual(values = c("red", "blue")) +  
  scale_y_continuous(labels = label_number(scale = 1, big.mark = ",")) + 
  theme(legend.position = "right")
print(final_plot_AI)
# Cognitive Science
Cognitive_Science <- subset(ted20, ted20$dominant_topic == '6')
Cognitive_Science <- glm.nb(like_count ~ year * Gender + duration + fame_google, data = Cognitive_Science)
summary(Cognitive_Science)
plot_CogSci <- interact_plot(Cognitive_Science, 
                             pred = year, 
                             modx = Gender,  
                             plot.points = FALSE,
                             interval = TRUE,           
                             colors = c("red", "blue"))

final_plot_Cog <- plot_CogSci + labs(x = "Year",                
                   y = "Number of Likes",     
                   color = "Gender") +        
  scale_color_manual(labels = c("Female", "Male"), values = c("red", "blue")) + 
  scale_fill_manual(values = c("red", "blue")) +  
  scale_y_continuous(labels = label_number(scale = 1, big.mark = ",")) + 
  theme(legend.position = "right")
print(final_plot_Cog)
# Social Justice & Activism
Social_Justice <- subset(ted20, ted20$dominant_topic == '10')
Social_Justice <- glm.nb(like_count ~ year * Gender + fame_google, data = Social_Justice)
summary(Social_Justice)
plot_Social_Justice <- interact_plot(Social_Justice, 
                                     pred = year, 
                                     modx = Gender,  
                                     plot.points = FALSE,
                                     interval = TRUE,           
                                     colors = c("red", "blue"))

final_plot_SJ <- plot_Social_Justice + labs(x = "Year",                
                           y = "Number of Likes",     
                           color = "Gender") +        
  scale_color_manual(labels = c("Female", "Male"), values = c("red", "blue")) + 
  scale_fill_manual(values = c("red", "blue")) +  
  scale_y_continuous(labels = label_number(scale = 1, big.mark = ",")) + 
  theme(legend.position = "right")
print(final_plot_SJ)
# Personal Growth
Personal_Growth <- subset(ted20, ted20$dominant_topic == '12')
Personal_Growth <- glm.nb(like_count ~ year * Gender + duration + fame_google, data = Personal_Growth)
summary(Personal_Growth)
plot_Personal_Growth <- interact_plot(Personal_Growth, 
                                      pred = year, 
                                      modx = Gender,  
                                      plot.points = FALSE,
                                      interval = TRUE,           
                                      colors = c("red", "blue"))

final_plot_PG <- plot_Personal_Growth + labs(x = "Year",                
                            y = "Number of Likes",     
                            color = "Gender") +        
  scale_color_manual(labels = c("Female", "Male"), values = c("red", "blue")) + 
  scale_fill_manual(values = c("red", "blue")) +  
  scale_y_continuous(labels = label_number(scale = 1, big.mark = ",")) + 
  theme(legend.position = "right")
print(final_plot_PG)
# Gender & Sexuality
Gender_Sexuality <- subset(ted20, ted20$dominant_topic == '14')
Gender_Sexuality <- glm.nb(like_count ~ year * Gender + duration + fame_google, data = Gender_Sexuality)
summary(Gender_Sexuality)
plot_Gender_Sexuality <- interact_plot(Gender_Sexuality, 
                                       pred = year, 
                                       modx = Gender,  
                                       plot.points = FALSE,
                                       interval = TRUE,           
                                       colors = c("red", "blue"))

final_plot_GS <- plot_Gender_Sexuality + labs(x = "Year",                
                             y = "Number of Likes",     
                             color = "Gender") +        
  scale_color_manual(labels = c("Female", "Male"), values = c("red", "blue")) + 
  scale_fill_manual(values = c("red", "blue")) +  
  scale_y_continuous(labels = label_number(scale = 1, big.mark = ",")) + 
  theme(legend.position = "right")
print(final_plot_GS)
# Mental Health
Mental_Health <- subset(ted20, ted20$dominant_topic == '15')
Mental_Health <- glm.nb(like_count ~ year * Gender + duration + fame_google, data = Mental_Health)
summary(Mental_Health)
plot_Mental_Health <- interact_plot(Mental_Health, 
                                    pred = year, 
                                    modx = Gender,  
                                    plot.points = FALSE,
                                    interval = TRUE,           
                                    colors = c("red", "blue"))

final_plot_MH <- plot_Mental_Health + labs(x = "Year",                
                          y = "Number of Likes",     
                          color = "Gender") +        
  scale_color_manual(labels = c("Female", "Male"), values = c("red", "blue")) + 
  scale_fill_manual(values = c("red", "blue")) +  
  scale_y_continuous(labels = label_number(scale = 1, big.mark = ",")) + 
  theme(legend.position = "right")
print(final_plot_MH)

# Culture
Culture <- subset(ted20, ted20$dominant_topic == '17')
Culture <- glm.nb(like_count ~ year * Gender + duration + fame_google, data = Culture)
summary(Culture)
plot_Culture <- interact_plot(Culture, 
                              pred = year, 
                              modx = Gender,  
                              plot.points = FALSE,
                              interval = TRUE,           
                              colors = c("red", "blue"))

final_plot_C <- plot_Culture + labs(x = "Year",                
                    y = "Number of Likes",     
                    color = "Gender") +        
  scale_color_manual(labels = c("Female", "Male"), values = c("red", "blue")) + 
  scale_fill_manual(values = c("red", "blue")) +  
  scale_y_continuous(labels = label_number(scale = 1, big.mark = ",")) + 
  theme(legend.position = "right")
print(final_plot_C)


##Robustness Checks 
#This is an example model that controls for speaker's fame as well as number of male and female speakers in all talks per topic.

speaker_counts <- ted20 %>%
  group_by(year, Gender) %>%
  summarise(count = n(), .groups = 'drop')

# Reshape the data to have separate columns for male and female counts
speaker_counts_wide <- speaker_counts %>%
  pivot_wider(names_from = Gender, values_from = count, values_fill = 0)

# Rename columns for easier reference
colnames(speaker_counts_wide) <- c("year", "female_count", "male_count")

# Join this back to your original dataset
data <- left_join(ted20, speaker_counts_wide, by = "year")

dom_topic1 <- subset(data, data$dominant_topic == '5')
model <- glm.nb(like_count ~ Gender * year +  female_count + male_count + duration +fame_google, data = dom_topic1)
summary(model)
plot_AI <- interact_plot(model, 
                         pred = year, 
                         modx = Gender,  
                         plot.points = FALSE,
                         interval = TRUE,           
                         colors = c("red", "blue"))
plot_AI + labs(x = "Year",                
               y = "Number of Likes",     
               color = "Gender") +        
  scale_color_manual(labels = c("Female", "Male"), values = c("red", "blue")) + 
  scale_fill_manual(values = c("red", "blue")) +  
  scale_y_continuous(labels = label_number(scale = 1, big.mark = ",")) + 
  theme(legend.position = "right")
```
```{r}

#View Count

# AI Related Topic
AIandRobotics <- subset(ted20, ted20$dominant_topic == '5')
AIandRobotics <- glm.nb(view_count ~ year * Gender + duration, data = AIandRobotics)
summary(AIandRobotics)
plot_AI <- interact_plot(AIandRobotics, 
                         pred = year, 
                         modx = Gender,  
                         plot.points = FALSE,
                         interval = TRUE,           
                         colors = c("red", "blue"))

plot_AI + labs(x = "Year",                
               y = "Number of Likes",     
               color = "Gender") +        
  scale_color_manual(labels = c("Female", "Male"), values = c("red", "blue")) + 
  scale_fill_manual(values = c("red", "blue")) +  
  scale_y_continuous(labels = label_number(scale = 1, big.mark = ",")) + 
  theme(legend.position = "right")

# Cognitive Science
Cognitive_Science <- subset(ted20, ted20$dominant_topic == '6')
Cognitive_Science <- glm.nb(like_count ~ year * Gender + duration, data = Cognitive_Science)
summary(Cognitive_Science)
plot_CogSci <- interact_plot(Cognitive_Science, 
                             pred = year, 
                             modx = Gender,  
                             plot.points = FALSE,
                             interval = TRUE,           
                             colors = c("red", "blue"))

plot_CogSci + labs(x = "Year",                
                   y = "Number of Likes",     
                   color = "Gender") +        
  scale_color_manual(labels = c("Female", "Male"), values = c("red", "blue")) + 
  scale_fill_manual(values = c("red", "blue")) +  
  scale_y_continuous(labels = label_number(scale = 1, big.mark = ",")) + 
  theme(legend.position = "right")

# Social Justice & Activism
Social_Justice <- subset(ted20, ted20$dominant_topic == '10')
Social_Justice <- glm.nb(like_count ~ year * Gender + duration, data = Social_Justice)
summary(Social_Justice)
plot_Social_Justice <- interact_plot(Social_Justice, 
                                     pred = year, 
                                     modx = Gender,  
                                     plot.points = FALSE,
                                     interval = TRUE,           
                                     colors = c("red", "blue"))

plot_Social_Justice + labs(x = "Year",                
                           y = "Number of Likes",     
                           color = "Gender") +        
  scale_color_manual(labels = c("Female", "Male"), values = c("red", "blue")) + 
  scale_fill_manual(values = c("red", "blue")) +  
  scale_y_continuous(labels = label_number(scale = 1, big.mark = ",")) + 
  theme(legend.position = "right")

# Personal Growth
Personal_Growth <- subset(ted20, ted20$dominant_topic == '12')
Personal_Growth <- glm.nb(like_count ~ year * Gender + duration, data = Personal_Growth)
summary(Personal_Growth)
plot_Personal_Growth <- interact_plot(Personal_Growth, 
                                      pred = year, 
                                      modx = Gender,  
                                      plot.points = FALSE,
                                      interval = TRUE,           
                                      colors = c("red", "blue"))

plot_Personal_Growth + labs(x = "Year",                
                            y = "Number of Likes",     
                            color = "Gender") +        
  scale_color_manual(labels = c("Female", "Male"), values = c("red", "blue")) + 
  scale_fill_manual(values = c("red", "blue")) +  
  scale_y_continuous(labels = label_number(scale = 1, big.mark = ",")) + 
  theme(legend.position = "right")

# Gender & Sexuality
Gender_Sexuality <- subset(ted20, ted20$dominant_topic == '14')
Gender_Sexuality <- glm.nb(like_count ~ year * Gender + duration, data = Gender_Sexuality)
summary(Gender_Sexuality)
plot_Gender_Sexuality <- interact_plot(Gender_Sexuality, 
                                       pred = year, 
                                       modx = Gender,  
                                       plot.points = FALSE,
                                       interval = TRUE,           
                                       colors = c("red", "blue"))

plot_Gender_Sexuality + labs(x = "Year",                
                             y = "Number of Likes",     
                             color = "Gender") +        
  scale_color_manual(labels = c("Female", "Male"), values = c("red", "blue")) + 
  scale_fill_manual(values = c("red", "blue")) +  
  scale_y_continuous(labels = label_number(scale = 1, big.mark = ",")) + 
  theme(legend.position = "right")

# Mental Health
Mental_Health <- subset(ted20, ted20$dominant_topic == '15')
Mental_Health <- glm.nb(like_count ~ year * Gender + duration, data = Mental_Health)
summary(Mental_Health)
plot_Mental_Health <- interact_plot(Mental_Health, 
                                    pred = year, 
                                    modx = Gender,  
                                    plot.points = FALSE,
                                    interval = TRUE,           
                                    colors = c("red", "blue"))

plot_Mental_Health + labs(x = "Year",                
                          y = "Number of Likes",     
                          color = "Gender") +        
  scale_color_manual(labels = c("Female", "Male"), values = c("red", "blue")) + 
  scale_fill_manual(values = c("red", "blue")) +  
  scale_y_continuous(labels = label_number(scale = 1, big.mark = ",")) + 
  theme(legend.position = "right")

# Culture
Culture <- subset(ted20, ted20$dominant_topic == '17')
Culture <- glm.nb(like_count ~ year * Gender + duration, data = Culture)
summary(Culture)
plot_Culture <- interact_plot(Culture, 
                              pred = year, 
                              modx = Gender,  
                              plot.points = FALSE,
                              interval = TRUE,           
                              colors = c("red", "blue"))

plot_Culture + labs(x = "Year",                
                    y = "Number of Likes",     
                    color = "Gender") +        
  scale_color_manual(labels = c("Female", "Male"), values = c("red", "blue")) + 
  scale_fill_manual(values = c("red", "blue")) +  
  scale_y_continuous(labels = label_number(scale = 1, big.mark = ",")) + 
  theme(legend.position = "right")


```
